Simple and Transparent Macroeconomic Distributional Forecasts

### 2023-09-26 presentation/presentation.tex
update presentation plots and notes

\title[Simple Prediction Intervals]{Simple and Transparent Macroeconomic Prediction Intervals}
\subtitle{} 
\author[Friederike Becker, Fabian Krüger, Melanie Schienle]{Friederike Becker, Fabian Krüger, Melanie Schienle}

@@

\begin{frame}[t]{Contributions of this work}
\begin{itemize}
    \item simple and transparent method of attaching prediction intervals 
\item show that attaching distributional forecasts to an existing
\item evaluate on years 1999-2021
\end{itemize}
\end{frame}

@@

\section{Methods}
\begin{frame}{Methods}
We apply an attractively simple and cheap method. For a given country and target:
\begin{itemize}
    \item given forecasts $\hat{y}_{t, h}$ and the realized true values $y_{t}$ ...
    \begin{itemize}
        \item for target year $t$, horizon $h$
    \end{itemize}
    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-9 \leq t^* < t \}$, containing the last nine forecast errors
    \begin{itemize}
        \item based on \textit{absolute} errors $\hat{e} = |y_{t} - \hat{y}_{t, h}| $
        \item sets are stratified by country, target and horizon
    \end{itemize}
    \item for $\alpha \in \{0.5, 0.8\}$, compute $q^{\alpha}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \alpha \right)$
    \item and compute the upper and lower endpoints of a central prediction interval as 
    \begin{itemize}
        \item $u^{\alpha}_{t,h} = \hat{y}_{t, h} + q^{\alpha}_{t, h}$ 
        \item $l^{\alpha}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\alpha}_{t, h}$
    \end{itemize}
\end{itemize}

@@

\begin{frame}{Benchmarks}
    We compare with benchmarks:
\begin{enumerate}
    \item same methodology, alternative point forecasts
    \begin{itemize}
        \item autoregressive (AR) model
        \item Primiceri Bayesian vector autoregressive (BVAR) model
    \end{itemize}
    \item directly generated distributional forecasts
    \begin{itemize}
        \item obtained from the BVAR model
    \end{itemize}
\end{enumerate}
\begin{itemize}
    \item trained on quarterly data, with \textit{slight informational advantage - specify this!} 
\end{itemize}

@@

\begin{frame}{Robustness Checks}
\textit{each will be linked to a short slide in Appendix giving the alternative results}
\begin{itemize}
    \item error extraction method: absolute vs. directional errors
    \item window method
    \item potential dependency of results on quantile extraction \\
    \textit{what I mean by this: does the fact that we are extracting quantiles from the samples influence the results? Show results for sample-based CRPS}
\end{itemize}
\end{frame}

@@

\begin{frame}{Summing up}
\begin{itemize}
\item Attaching distributional forecasts via past forecast errors to an existing base of point forecasts is
    \begin{itemize}
        \item cheap
        \item competitive
        \item transparent
    \end{itemize}
\item Attachment of uncertainty to point forecasts is often substantial, making its communication necessary
\item IMF forecasts are valuable source for distributional forecasts in their own right \bigskip \\
\item     Outlook
    \begin{itemize}
        \item employ method that ideally utilizes the cross-section dimension, e.g. via Hierarchical Bayesian Modeling
    \end{itemize}

@@

\appendix
\beginbackup

>>>>

\title[Simple Prediction Intervals]{Simple and Transparent Macroeconomic Distributional Forecasts}
\subtitle{} 
\author[Friederike Becker, Fabian Krüger, Melanie Schienle]{Friederike Becker, Fabian Krüger, Melanie Schienle}

@@

\begin{frame}[t]{Contributions of this work}
\begin{itemize}
    \item show that attaching prediction intervals to an existing base of point forecasts can be 
    \begin{itemize} 
    \item simple
    \item cheap
    \end{itemize}   
    \item provide solidly performing distributional forecasts for 
    \begin{itemize}
    \item  GDP growth and inflation
    \item  all G7 countries
    \item  current and next year 
    \end{itemize}
    %\item simple and transparent method of attaching prediction intervals 
%\item show that attaching distributional forecasts to an existing
%\item for up to one and a half years into the future 
%\item evaluate on years 1999-2021
\end{itemize}
\end{frame}

@@

\section{Methods}
\begin{frame}{Methods}
We apply an attractively simple and cheap method. For a given country and target:
\begin{itemize}
    \item given forecasts $\hat{y}_{t, h}$ and the realized true values $y_{t}$ ...
    \begin{itemize}
        \item for target year $t$, horizon $h$
    \end{itemize}
    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-9 \leq t^* < t \}$, containing the last nine forecast errors
    \begin{itemize}
        \item based on \textit{absolute} errors $\hat{e}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
        \item sets are stratified by country, target and horizon
    \end{itemize}
    \item for $\alpha \in \{0.5, 0.8\}$, compute $q^{\alpha}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \alpha \right)$
    \item and compute the upper and lower endpoints of a central prediction interval as 
    \begin{itemize}
        \item $u^{\alpha}_{t,h} = \hat{y}_{t, h} + q^{\alpha}_{t, h}$ 
        \item $l^{\alpha}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\alpha}_{t, h}$
    \end{itemize}
\end{itemize}

@@

\begin{frame}{Benchmarks}
    We compare with benchmarks:
\begin{enumerate}
    \item same methodology, alternative point forecasts
    \begin{itemize}
        \item autoregressive (AR) model
        \item Primiceri Bayesian vector autoregressive (BVAR) model
    \end{itemize}
    \item directly generated distributional forecasts
    \begin{itemize}
        \item obtained from the BVAR model
    \end{itemize}
\end{enumerate}
\begin{itemize}
    \item trained on quarterly data, with slight informational advantage
\end{itemize}

@@

\begin{frame}{Robustness Checks / Alternative Methods}
\begin{itemize}
    \item error extraction method: absolute vs. directional errors
    \begin{itemize}
    \item similar scores, worse calibration \hyperlink{errorextraction}{\beamerbutton{link}}
    \end{itemize}
    \item window method: rolling vs. expanding window
    \begin{itemize}
    \item slightly improved coverage and scores, at the cost of interpretability \hyperlink{extractionmethod}{\beamerbutton{link}}
    \end{itemize}
    \item potential dependency of results on quantile extraction \\
    \begin{itemize}
        \item ordering between forecasts remains the same with sample-based CRPS \hyperlink{samplecrps}{\beamerbutton{link}}
    \end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Summing up}
\begin{itemize}
\item Attaching distributional forecasts via past forecast errors to an existing base of point forecasts is
    \begin{itemize}
        \item cheap
        \item competitive
        \item transparent
    \end{itemize}
\item Uncertainty around point forecasts is often substantial, making its communication necessary
\item IMF forecasts are valuable source for distributional forecasts in their own right \bigskip \\
\item     Outlook
    \begin{itemize}
        \item employ method that ideally utilizes the cross-section dimension, e.g. via Hierarchical Bayesian Modeling
    \end{itemize}

@@

\appendix
\beginbackup
\begin{frame}{Directional Errors - Scores}
\label{errorextraction}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_directional.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}
\begin{frame}{Directional Errors - Coverage}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/coverage_directional.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}

\begin{frame}{Expanding Window - Scores}
\label{extractionmethod}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_ew.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}
\begin{frame}{Expanding Window - Coverage}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/coverage_ew.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}

\begin{frame}{CRPS by sample}
\label{samplecrps}
\begin{figure}
        \centering
        \includegraphics[width=0.7\textwidth]{figures/crpssample.png}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}
